\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=black,
  citecolor=black
}

\begin{enumerate}[leftmargin=*, label={[\arabic*]}]
  \item blup.in (2023). A Brief History of Flutter.           \url{https://www.blup.in/blog/a-brief-history-of-flutter}
  \item A. W. Junaid, “History and Evolution of Dart Programming Language,” \textit{awjunaid.com}, Sep. 13, 2023. [Online]. \url{https://awjunaid.com/dart/history-and-evolution-of-dart-programming-language/}.
  \item GeeksforGeeks (2025). Flutter Tutorial. \url{https://www.geeksforgeeks.org/flutter-tutorial/}
  \item Dart Tutorial - Learn Dart Programming. OOP in Dart. \url{https://dart-tutorial.com/object-oriented-programming/oop-in-dart/}
  \item viblo.asia. Những Widget cơ bản trong Flutter. \url{https://viblo.asia/p/nhung-widget-co-ban-trong-flutter-1Je5Eygy5nL}
  \item GeeksforGeeks (2023). Flutter – Stateful Widget. \url{https://www.geeksforgeeks.org/flutter-stateful-widget/}
  \item Flutter Docs (2025). Flutter architectural overview. \url{https://docs.flutter.dev/resources/architectural-overview}
  \item Bailey, T., \& Biessek, A. (2021). \textit{Flutter for Beginners – Second Edition: An introductory guide to building cross-platform mobile applications with Flutter 2.5 and Dart}.
  \item Tashildar, A., Shah, N., Gala, R., Giri, T., \& Chavhan, P. (2020). \textit{Application Development Using Flutter}. International Research Journal of Modernization in Engineering Technology and Science, 2(8). 
  \item Đại học Bách Khoa Hà Nội (2020). \textit{Slide bài giảng học phần IT4788 – Phát triển ứng dụng đa nền tảng}. \url{https://soict.daotao.ai/courses/course-v1:SoICT+IT4788+2020-2/about} 
  \item Rahul, I. \textit{All In One Flutter Book}. GitHub repository. \url{https://github.com/irahulcse/All_In_One_Flutter_Book}
\end{enumerate}
